\documentclass[11pt, a4paper]{article} % Changed back to 11pt

%----------------------------------------------------------------------------------------
%   PACKAGES
%----------------------------------------------------------------------------------------
\usepackage[utf8]{inputenc}     % Input encoding
\usepackage[T1]{fontenc}        % Font encoding
\usepackage{lmodern}            % Use Latin Modern fonts (RECOMMEND ADDING TO RESUME TOO)
\usepackage{geometry}           % For setting margins
\usepackage{parskip}            % Use vertical space between paragraphs (Kept for letter style)
\usepackage{url}                % Nicer URL formatting
\usepackage{hyperref}           % For clickable links - Load relatively late
\usepackage{microtype}          % Improves typography
\usepackage{textcomp}           % Added for potential symbols (like ® if needed)

%----------------------------------------------------------------------------------------
%   PAGE STYLE & GEOMETRY
%----------------------------------------------------------------------------------------
% USE SAME MARGINS AS RESUME (Even with different font size, this keeps the frame consistent)
\geometry{left=0.75in, right=0.75in, top=0.6in, bottom=0.6in}
\pagestyle{empty}               % No page numbers

%----------------------------------------------------------------------------------------
%   HYPERLINK SETUP (Copied from Resume)
%----------------------------------------------------------------------------------------
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Man Yan Chan Cover Letter}, % Optional: Add PDF metadata
    pdfauthor={Man Yan Chan}        % Optional: Add PDF metadata
}
% \urlstyle{same} % Optional: uncomment if you want URLs to be black like text

%----------------------------------------------------------------------------------------
%   DOCUMENT START
%----------------------------------------------------------------------------------------
\begin{document}

%----------------------------------------------------------------------------------------
%   HEADER: Your Name and Contact Information (MATCHING RESUME STYLE)
%----------------------------------------------------------------------------------------
\begin{center} % Center the whole header block
    {\Huge\bfseries Man Yan CHAN} \\ \vspace{1.5mm} % Name (same style as resume)
    % Centered contact info line (same as resume)
    Eastern District, Hong Kong \quad|\quad +852 56924792 \quad|\quad \href{mailto:richard.mychan@gmail.com}{richard.mychan@gmail.com} \\
    % Add optional centered links line if desired (matching resume possibility)
    % \href{https://www.linkedin.com/in/richard-chanmy}{LinkedIn} \quad|\quad \href{https://github.com/manyan-chan}{Github} \quad|\quad \href{https://manyan-chan.github.io}{Portfolio}
\end{center}
\vspace{2ex} % Adjust space after header (using relative unit)

%----------------------------------------------------------------------------------------
%   DATE
%----------------------------------------------------------------------------------------
% \noindent % No longer needed before Date if using parskip
% \today % Or specific date: May 28, 2024

\bigskip % Standard vertical space (parskip handles space before this)

%----------------------------------------------------------------------------------------
%   RECIPIENT ADDRESS (Add if known)
%----------------------------------------------------------------------------------------
% [Hiring Manager Name, Title] \\ % <<<--- REPLACE OR REMOVE
% [Company Name] \\               % <<<--- REPLACE OR REMOVE
% [Company Street Address] \\     % <<<--- REPLACE OR REMOVE
% [Company City, Postal Code]     % <<<--- REPLACE OR REMOVE
%
% \bigskip % Add space after recipient address if used

%----------------------------------------------------------------------------------------
%   SALUTATION
%----------------------------------------------------------------------------------------
% \noindent % No longer needed before Salutation if using parskip
Dear Hiring Manager, % Or "Dear [Mr./Ms./Mx. Last Name]," if known

\medskip % Standard smaller vertical space after salutation (parskip handles space before)

%----------------------------------------------------------------------------------------
%   LETTER BODY (Your content remains unchanged)
%   Paragraphs will have vertical space between them due to 'parskip'.
%   No indentation needed. Font size is now 11pt.
%----------------------------------------------------------------------------------------
I am writing to express my strong interest in contributing my skills as a results-driven Software Engineer to your esteemed organization. With over three years of dedicated experience in developing and optimizing software solutions within the dynamic financial sector, I possess a proven track record of delivering high-quality, scalable code that significantly enhances operational performance and addresses complex business challenges.

My background, combining a BBA in Information Systems and Computer Science from The University of Hong Kong, provides a unique perspective, enabling me to seamlessly bridge the gap between intricate technical requirements and core business objectives. I am highly proficient in Python and its data science ecosystem (Pandas, NumPy, Matplotlib), alongside SQL and JavaScript, applying these skills across the full development lifecycle. My experience spans critical areas within finance, including developing and maintaining FIX protocol interfaces for electronic trading in equities derivatives, creating optimized ETL workflows for treasury functions, and building robust backtesting frameworks and real-time dashboards for quantitative strategies.

Throughout my roles at leading financial institutions like Barclays and HSBC, as well as in a dynamic FinTech environment at NineBarrack, I have consistently focused on tangible results. I have successfully collaborated with cross-functional teams, including sales and trading desks, to enhance electronic trading capabilities and competitiveness. My work has involved streamlining processes through automation, reducing data processing times significantly, and leveraging modern web technologies (Dash, Flask, ReactJS, SocketIO) and cloud platforms (AWS EC2) to deliver interactive applications and ensure system reliability. Furthermore, my commitment to quality is underscored by my experience in developing comprehensive test strategies (SIT/UAT) and utilizing CI/CD practices (TeamCity, Jenkins, Git).

My strong understanding of financial markets, encompassing Equities, FICC, and Derivatives, complements my technical expertise. I am adept at transforming complex financial logic into robust software solutions and thrive in fast-paced environments that demand innovation, collaboration, and a relentless focus on efficiency and performance. My extensive list of certifications further attests to my commitment to continuous learning and professional development within both technology and finance.

I am confident that my technical skills, financial domain knowledge, and proactive approach align well with the requirements of challenging software engineering roles. I am eager to leverage my experience to contribute to your team's success. Thank you for considering my application. My resume, providing further detail on my qualifications and accomplishments, is attached for your review. I look forward to the possibility of discussing how I can add value to your organization.

%----------------------------------------------------------------------------------------
%   CLOSING
%----------------------------------------------------------------------------------------
\medskip % Add a little space before the closing
Sincerely,

\vspace{3\baselineskip} % Space for signature (adjust height as needed)

%----------------------------------------------------------------------------------------
%   SIGNATURE NAME
%----------------------------------------------------------------------------------------
Man Yan Chan % \noindent is not needed here due to parskip

%----------------------------------------------------------------------------------------
%   DOCUMENT END
%----------------------------------------------------------------------------------------
\end{document}